### 2016-08-26 ms/ms.tex
changed the final verison of the ms, added the svg files for the sanky plots figure

\begin{abstract}
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network assembly, therefore,
  is a priority for system-level conservation biology. We explore the
  assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. Species are highly
  dynamic in their positions in the networks, such that we find that
  assembly is punctuated by significant reorganizations of
  interactions. Non-assembling mature hedgerows and weedy field
  margins did not undergo as many network reorganizations, suggesting
  environmental factors alone cannot account for the changes observed
  in assembling communities. Pollinator species were highly
  opportunistic, and in fact the most persistent and generalized
  species were most variable in their network positions --- the
  opposite of what would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turn over
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Assembling networks also increased in nestedness through
  time, though this did not make them more robust to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The most widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some evidence that
assembly occurred through preferential attachment. Network nestedness,
a pattern of interactions where a generalist core interacts with both
specialist and generalist species, increased as the community aged
\citep{albrecht2010plant}. Increasing nestedness could result from
preferential attachment process where specialist species attach to the
well-connected, generalist core.  % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}.  In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating network restoration is especially imperative in areas
where species interactions provide essential ecosystem services, such
as crop pollination. In intensively managed agricultural landscapes,
the demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure provision the continued provision of ecosystem services and
curb biodiversity loss, effective restoration of pollinators and their
interactions in agricultural landscapes is critical.

@@

Using a long-term dataset of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics in the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows we planted along field
margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models --- one where a change point
occurred between two networks, and one where no change occurred ---
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of eight years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. We employed
code published online by L.~Peel for the change point
analysis. Analyses we conducted in Python 3.4.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their role
and thus contribute more strongly to network reorganization. We test
whether the more persistent species with the highest degree are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculate species persistence as the proportion of surveys a plant
or pollinator is observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations from an extensive dataset
from Yolo County (approx.~18000 interaction records) that included
both the data included in this study and additional data from sites
where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness at each site through time. Closeness describes the
centrality of a species in the network by calculating path lengths to
other vertices (species) in the graph. We use linear mixed models to
test whether the species closeness variability (log) is related to the
persistence or degree of that species \citep{lme4, lmetest}. We
included random effects for species, as well as site. Because the
degree and persistence of pollinators were strongly correlated, ($\rho
= 0.84$, $p$-value $<$ $2*10^{-16}$), we include each explanatory
variable in the model separately. Plant degree and persistent were not
significantly correlated, but we use the same models as we did for the
pollinators for consistency. A linear increase in closeness, as might
be expected with assembly by preferential attachment, would also lead
to a high variability in closeness scores, so we test whether
closeness increases through time.

@@

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. Assembling networks may have higher
rates of pollinator turnover than non-assembling communities because
new pollinator species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities. In
addition, at assembling hedgerows, plants may ``colonize'' the
networks as they become more attractive resources.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more turnover of
species and interactions than non-assembling communities, the species
and interaction temporal turnover estimates were included as response
variables in a linear mixed models with site type as an explanatory
variable along with a random effect of site \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develop a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- is also expected to increase as species
preferentially attach to the core. \flagged{Is this true?} Lastly, the
network specialization may change as the community assembles. If
specialist species colonize the network or species begin to limit
their interaction niche breath as the network assembles, network-level
specialization will increase \citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. We evaluate network specialization with the
metric H2, which estimates the deviation of the observed interaction
frequency between plants and pollinators from a null expectation where
all partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from zero for generalized networks
to one for specialized networks.

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ standard error
of the estimate, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or
abundance ($0.001 \pm 0.003$, $p$-value=$0.65$, Fig.~\ref{fig:rob}).

In contrast, the robustness of networks to cascading perturbations, as
measured by the algebraic connectivity of the network, increased as
the network assembled (estimate of the slope of robustness to
cascading perturbations through time $\pm$ standard error of the
estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$, Fig.~\ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and few consistent trends in when change points occurred
across all sites. Several sites had network changing points between
years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. The assembling hedgerows
were not sampled in 2010, so disentangling whether the changing points
are due to skipping a year of assembly or the drought is not
possible. Interestingly, most assembling hedgerows did not undergo a
significant interaction reorganization immediately after a hedgerow
was planted (i.e., the transition from weedy field margin to
hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have an
impact on the plant-pollinator communities (Kremen and M'Gonigle, in
prep).

In addition to finding multiple network organization changing points
during assembly, the species that contribute most to those
reorganizations were not what is expected by preferential
attachment. Based on a preferential attachment-like mechanism, we
expect that the most persistent and high degree species would remain
stable in the network core during assembly. Surprisingly, however, we
encountered the opposite pattern. For example, the five most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed what module (i.e., community) of which
they were a member across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be able to better exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also most persistent. More persistent species also
have longer phenologies, so they can visit many different flowers,
resulting in a higher degree. Either way, our result suggests that
adaptable species can change their network position to utilize the
most advantageous floral resources available, which may depend on the
other pollinator species that are present and the state of the plant
community. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

@@

The frequent changing points in network organization, dynamic nature
of species positions in the networks, and turnover of species and
interactions all point to an assembly mechanism other than
preferential attachment. Nestedness did increase with years
post-restoration, as would be expected if colonizing, specialist
species attached to a central, generalist core
\citep{albrecht2010plant}. With preferential attachment, however, we
would also expect connectance and specialization to increase, and we
found no such trends. \flagged{Wait if connectance increases doesn't
  that mean specialization decreases? Which would we expect to change
  with preferential attachment?} The stable level of network-level
specialization through the assembly process may be due to the
increased colonization of specialized species \citep{mgonigle-2015-x}
accompanied by an increase in the diet breath of resident
species. This would be expected if resident species were able to
minimize their foraging time by expanding their diet breath as plant
diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

>>>>

\begin{abstract} %% Lauren - I would invert the phrase just so it does not beging with metwork structure - "communities' ability to maintain function in the face of species extinction is related to the structure fo networks". 
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network assembly, therefore,
  is a priority for system-level conservation biology. We explore how the
  assembly of plant-pollinator communities occured, on native plant
  restorations in the Central Valley of California. Species are highly
  dynamic in their positions in the networks, resulting in a community 
  assembly punctuated by significant reorganizations of
  interactions. Non-assembling mature hedgerows and weedy field
  margins did not undergo as many significant network reorganizations, suggesting
  environmental factors alone cannot account for the changes observed
  in assembling communities. Pollinator species were highly
  opportunistic, and in fact the most persistent and generalized
  species were most variable in their network positions --- the
  opposite of what would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} also found some evidence that
assembly occurred through preferential attachment. Network nestedness,
a pattern of interactions where a core formed by generalist species that interact with both
specialist and generalist species, increased as the community aged
\citep{albrecht2010plant}. Thus, an increase in nestedness could result from
preferential attachment process where specialist species attach to the
well-connected, generalist core.  % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the ordered network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}.  In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the species behavior.

%% restoration
%% Lauren, I would combine this paragraph with the next one, because is too short. I tried to think of stuff to add, but I coulnd't...
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating network restoration is especially imperative in areas
where species interactions provide essential ecosystem services, such
as crop pollination. In intensively managed agricultural landscapes,
the demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and
curb biodiversity loss, it is critical to effective restore pollinators and their
interactions in agricultural landscapes.

@@

%% Lauren I would put 10 year dataset; and I *loved* the way you organized the ideas here!! 
We explore the process of network development using a long-term dataset of plant-pollinator communities assembling following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley.  We first determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics in the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows communities (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows we planted along field
margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models --- one where a change point
occurred between two networks, and one where no change occurred ---
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of eight years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. We employed
code published online by L.~Peel for the change point
analysis. Analyses were conducted in Python 3.4.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their position
and thus contribute more strongly to network reorganization. We test
whether the more persistent species with the highest degree (number of interactions) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculate species persistence as the proportion of surveys in which a plant
or pollinator is observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations from an extensive dataset
from Yolo County (approx.~18000 interaction records) that included
both the data included in this study and additional data from sites
where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness at each site through time. Closeness describes the
centrality of a species in the network by calculating path lengths to
other vertices (species) in the graph. We use linear mixed models to
test whether the species closeness variability (log) is related to the
persistence or degree of that species \citep{lme4, lmetest}. We
included random effects for species, as well as site. Because the
degree and persistence of pollinators were strongly correlated, ($\rho
= 0.84$, $p$-value $<$ $2*10^{-16}$), we include each explanatory
variable in the model separately. Plant degree and persistence were not
significantly correlated, but we use the same models as we did for the
pollinators for consistency. A linear increase in closeness, as might
be expected with assembly by preferential attachment, would also lead
to a high variability in closeness scores, so we test whether
closeness increases through time.

@@

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may have higher
rates of pollinator turnover than non-assembling communities because
new pollinator species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities. In
addition, at assembling hedgerows, plants may ``colonize'' the
networks as they become more attractive resources, and establish new interactions with pollinators.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that, which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more species and interactions turnover than non-assembling communities, the species
and interaction temporal turnover estimates were included as response
variables in a linear mixed model with site type as an explanatory
variable along with site as a random effect \citep{lme4, lmetest}.

%% Lauren I like this paragraph, but I think we could use a figure in the supplementary to help the reader understand... maybe a schematic representation? I'll try and think of something 
Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develop a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would decrease as new, specialist species,
preferentially attach to the core. \flagged{Is this true? - I think that the relationship between richness and connectance is not clear, i changed to decrease because it makes more sense via preferential attachment - the denominator increases because spp are being added, but the number of links does not, because they are specialists --- I checked with Paulo and he agrees} Lastly, the overall level of
network specialization may change as the community assembles. Network-level
specialization will increase if
specialist species colonize the network or species begin to limit
their interaction niche breath as the network assembles  \citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared across communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. We evaluate network specialization with the
metric H2, which estimates the deviation of the observed interaction
frequency between plants and pollinators from a null expectation where
all partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from zero for generalized networks
to one for specialized networks.

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ standard error
of the estimate, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or
abundance ($0.001 \pm 0.003$, $p$-value=$0.65$, Fig.~\ref{fig:rob}). In contrast, the robustness of networks to cascading perturbations, as
measured by the algebraic connectivity of the network, increased as
the network assembled (estimate of the slope of robustness to
cascading perturbations through time $\pm$ standard error of the
estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$, Fig.~\ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing points. These network organizations
are unlikely a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and few consistent trends in when change points occurred
across all sites. Several sites had network changing points between
years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. The assembling hedgerows
were not sampled in 2010, so disentangling whether the changing points
are due to skipping a year of assembly or the drought is not
possible. Interestingly, most assembling hedgerows did not undergo a
significant interaction reorganization immediately after a hedgerow
was planted (i.e., the transition from weedy field margin to
hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have an
impact on the plant-pollinator communities (Kremen and M'Gonigle, in
prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was different from what is expected by preferential attachment. Based on a preferential attachment mechanism \flagged{process instead of mechanism?}, we expect that the most persistent and high degree species would remain
stable in the network core during assembly. Surprisingly, however, we
encountered the opposite pattern. For example, the five most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module (i.e., community)
they were a member across years in all the assembling
hedgerows. Because species degree and persistence were strongly
correlated, it is difficult to disentangle the causal mechanism for
why species with those characteristics are so variable in their
network position. Generalized species may be able to better exploit
the limited floral resources in the intensively managed agriculture
landscape, and thus also be the most persistent. More persistent species usually 
have longer phenologies, so they can visit many different flowers,
resulting in a higher degree. Either way, our result suggests that
adaptable species can change their network position to utilize the
most advantageous floral resources available, which may depend on the
other pollinator species that are present, and the state of the plant
community. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

@@

When we look at the network-level metrics to explore the mechanism through which the community is assembling, we encounter that nestedness did increase with years
post-restoration, as would be expected if colonizing, specialist
species attached to a central, generalist core
\citep{albrecht2010plant}, as predicted by preferential attachment. In addition, connectance decreased, as would be expected if the network is being colonized by specialist species and the overall mean number of interactions per species did not change. With preferential attachment, however, we
would also expect specialization to increase, and we
found no such trend. Furtheremore, the frequent changing points in network organization, dynamic nature
of species positions in the networks, and turnover of species and
interactions all point to an assembly mechanism other than
preferential attachment.  The stable level of network-level
specialization through the assembly process may be due to the
increased colonization of specialized species \citep{mgonigle-2015-x}
accompanied by an increase in the diet breath of resident
species. This would be expected if resident species were able to
minimize their foraging time by expanding their diet breath as plant
diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.
